Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-12 chapters/paper3.tex
Fixed caption for new images and fixed rheology property table

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
    \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
             a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
             state is reached.} 
    \label{fig:stress_time} 
\end{figure}

@@

\begin{table}[h!]
    \centering
    \renewcommand{\arraystretch}{1.5}  % Increases row height
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Bulkley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. We show that upon application of shear
             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
             large variations in the interface angle.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. We show that upon application of shear
             particles tilt out of the interface reduces the interfacial area stabilized.} 
    \label{fig:interface_angle_shear} 
\end{figure}

>>>>

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
    \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
             a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
             state is reached, with pseudo-steady states being obtained from the regions with the circular markers.} 
    \label{fig:stress_time} 
\end{figure}

@@

\begin{table}[h!]
    \centering
    \renewcommand{\arraystretch}{1.5}  % Increases row height
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.570 & 0.946 & $9.818 \cdot 10^{-5}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.5601 & 0.920 & $4.591 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.608 & 0.920 & $1.937 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.630 & 0.922 & $1.188 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.559 & 0.946 & $4.057 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.602 & 0.939 & $4.360 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.583 & 0.921 & $3.914 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.605 & 0.868 & $6.153 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Bulkley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
             applied shear rate, particle ordering to the field and the particle shape.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
             interfacial tilting a function of the initial particle order and particle shape.} 
    \label{fig:interface_angle_shear} 
\end{figure}
